Exercise 3: Software Architecture in Practice Case: Beer Web Store

### 2008-03-17 trunk/SAiP/Module1/H3/doc/productlines.tex
Adding label
Adding spell-check

%%%
% Product Lines and Frameworks
%%%
\section{Product Lines -- Beer Web Store}
Consider a Beer Web Store for buying specialty beers. The software
architect has designed a deployment structure of the system as shown
below:
\begin{figure}[h!]
  \centerline{\epsfig{figure=figures/bws-deployment,scale=0.80}}
  \label{fig:observation}
\end{figure}
The main architectural drivers for the system are performance and
modifiability and the following is the main use case for the system:
\begin{quote}
  The customer browses the beer catalogue for descriptions and
  reviews. The customer selects appropriate beers for purchase and
  these are added to his shopping basket. When the customer checks
  out, payment is validated through the payment service
\end{quote}

@@

\subsection{Product Lines - Question 2}

\begin{question}
Discuss the benefits and liabilities of using a product line
approach in relation to the case?
\end{question}

@@

Defining the product line architecture fully up front means a big investment in time and money in order to create the arcitecture and the first product based on it, so if it is the only product made, then it will go way over budget both in time and money. The idea is that creating the next product will be significantly cheaper, because a very large part of the products functionality is covered by the product line and very little (if any) redesign has to be done. As more and more products are created based on the product line their individual budget savings will help pay for the initial investment, eventually leading to a profit compared to building the products from scratch each time.

@@

The requirement that other product's such as other stamps or soda-pop should be suppoprted, means that the server's domain model and database must support general elements as opposed to just beer elements.

@@

It may now seem like SOA is the answer to creatign a product line, yet this is not the case. It is very possible to create very specific services, like the "Beer look-up service", and this may be just fine for a Beer Web Store based on SOA, yet this is not a product line. The same architectual consideration must be done when creating the elemenets of a product line and define their interrelations, must also be done when defining the services and their interrelations. The only "structure" that SOA imposes by definition is the loose coupling between the user and the service.

>>>>

%%%
% Product Lines and Frameworks
%%%
\section{Product Lines -- Beer Web Store}
Consider a Beer Web Store for buying speciality beers. The software
architect has designed a deployment structure of the system as shown
below:
\begin{figure}[h!]
  \centerline{\epsfig{figure=figures/bws-deployment,scale=0.80}}
  \label{fig:observation}
\end{figure}
The main architectural drivers for the system are performance and
modifiability and the following is the main use case for the system:
\begin{quote}
  The customer browses the beer catalogue for descriptions and
  reviews. The customer selects appropriate beers for purchase and
  these are added to his shopping basket. When the customer checks
  out, payment is validated through the payment service
\end{quote}

@@

\subsection{Product Lines - Question 2}
\label{sec:pl_q2}
\begin{question}
Discuss the benefits and liabilities of using a product line
approach in relation to the case?
\end{question}

@@

Defining the product line architecture fully up front means a big investment in time and money in order to create the architecture and the first product based on it, so if it is the only product made, then it will go way over budget both in time and money. The idea is that creating the next product will be significantly cheaper, because a very large part of the products functionality is covered by the product line and very little (if any) redesign has to be done. As more and more products are created based on the product line their individual budget savings will help pay for the initial investment, eventually leading to a profit compared to building the products from scratch each time.

@@

The requirement that other product's such as other stamps or soda-pop should be supported, means that the server's domain model and database must support general elements as opposed to just beer elements.

@@

It may now seem like SOA is the answer to creating a product line, yet this is not the case. It is very possible to create very specific services, like the "Beer look-up service", and this may be just fine for a Beer Web Store based on SOA, yet this is not a product line. The same architectural consideration must be done when creating the elements of a product line and define their interrelations, must also be done when defining the services and their interrelations. The only "structure" that SOA imposes by definition is the loose coupling between the user and the service.
